---
title: "Linear Regression Analysis and Visualisation"
format: html
---

```{r}
#| label: Install and Load Libraries
#| message: false
#| warning: false
#| include: false

# Install packages, load libraries
if(!require("tidyverse"))
  install.packages("tidyverse")
  library(tidyverse)

if(!require("DBI"))
  install.packages("DBI")
  library(DBI)

if(!require("RSQLite"))
  install.packages("RSQLite")
  library(RSQLite)

if(!require("kableExtra"))
  install.packages("kableExtra")
  library(kableExtra)

if(!require("DT"))
  install.packages("DT")
  library(DT)

if(!require("ggplot2"))
  install.packages("ggplot2")
  library(ggplot2)

if(!require("dplyr"))
  install.packages("dplyr")
  library(dplyr)

if(!require("broom"))
  install.packages("broom")
  library(broom)

# Connect to database
conn <- dbConnect(RSQLite::SQLite(), "virtual_production.db")

```

# Linear Regression Modelling

```{r}
#| label: Part 1 DB Query
#| message: true
#| warning: true
#| include: false

# Select information from production, title and budget, Count the unique crew members on each and assign value to production status from the Productions table and Join with Production Crew Table and group by ID, Title, Budget and Status

# Queries the database and runs part1
data <- dbGetQuery(conn, "SELECT Productions.ProductionID, Productions.Title, Productions.Budget, COUNT(DISTINCT ProductionCrew.CrewID) AS CrewSize, Productions.Status FROM Productions LEFT JOIN ProductionCrew ON Productions.ProductionID = ProductionCrew.ProductionID GROUP BY Productions.ProductionID, Productions.Title, Productions.Budget, Productions.Status;")

data <- data %>% mutate(SuccessRate = case_when(Status == "Completed" ~ 1, Status == "In Progress" ~ 0.5, TRUE ~ 0))

# Predict SuccessRate based on Budget & Crewsize using a linear model
model <- lm(SuccessRate ~ Budget + CrewSize, data = data)
summary(model)

```


```{r}
#| label: Part 1 Data Models
#| echo: false
#| message: true
#| warning: true

kable(data, caption = 'Summary') %>% kable_styling(full_width = FALSE, position = "center", bootstrap_options = c("striped", "hover"))

# Plot results of Budget vs Success Rate to a scatterplot chart
ggplot(data, aes(x = Budget, y = SuccessRate, colour = CrewSize)) + geom_point(size = 3) + geom_smooth(method = "lm", se = FALSE, colour = "blue") + labs(title = "Budget vs Success Rate", x = "Budget", y = "Success Rate (0-1 scale)", colour = "Crew Size") + theme_minimal()

# Plot results of Crew Size vs Success Rate to a scatterplot chart
ggplot(data, aes(x = CrewSize, y = SuccessRate)) + geom_point(size = 3, colour = "darkred") + geom_smooth(method = "lm", se = FALSE, colour = "black") + labs(title = "Crew Size vs Success Rate", x = "Crew Size", y = "Success Rate (0-1 scale)") + theme_minimal()

```

# Model Coefficients Interpretation

```{r}
#| label: Extract Coefficents
#| echo: false
#| message: true
#| warning: true
#| paged-print: true

# Extract coeffecients and display in a table
model_tidy <- tidy(model)
kable(model_tidy, caption = "Linear Regression Coefficients") %>% kable_styling(full_width = FALSE)

# Diagnostic Plots
par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))
```

```{r}
#| label: Disconnect from database
#| message: true
#| warning: true
#| include: false

dbDisconnect(conn)

```

# Discussion
The regression model suggests that both budget and crew size have a positive association with production success. Success rates of project completion are associated by the use of larger teams and higher budgets. The budget coefficient indicates that extra budget increases the predicted success rate by